Laplacian envelope

### 2021-11-13 Notes/laplace.tex
reordered notes

Note that models with the serial topology must satisfy detailed balance.
Therefore, the conjecture from \cref{sec:finite} implies that the square-root bound of \cref{sec:sqrt} applies, implying the stricter envelope of \cref{eq:envDB}.
In \cref{fig:envnum} we compare these theoretical envelopes with the numerical maximisation from \cref{fig:envnum}.
We can see that this conjectured envelope is close to tight, being off by a constant factor.

@@

\begin{figure}[tbp]
  \centering
  % Requires \usepackage{graphicx}
  \begin{myenuma}
  \item\aligntop{\includegraphics[width=0.45\linewidth,page=7]{envelope.pdf}}
  \item\aligntop{\includegraphics[width=0.45\linewidth,page=13]{envelope.pdf}}
  \item\aligntop{\includegraphics[width=0.45\linewidth,page=21]{envelope.pdf}}
  \item\aligntop{\includegraphics[width=0.45\linewidth,page=27]{envelope.pdf}}
  \item\aligntop{\includegraphics[width=0.45\linewidth,page=36]{envelope.pdf}}
  \item\aligntop{\includegraphics[width=0.45\linewidth,page=50]{envelope.pdf}}
  \end{myenuma}
  \caption[Optimal models]{The models that constitute the numeric envelope in \cref{fig:envnum}.
  The plot to the left of each frame indicates the memory curve of the model shown to the right in green, with the numeric envelope for models with the serial topology in orange and the proven envelope, \eqref{eq:env}, in blue.
  Above the left plot we have a graphical display of the model, described with more detail to the right.
  The area of each node is proportional to the steady state probability in that state and the thickness of the red and blue edges are proportional to the transition probabilities under potentiation and depression.
  The bar graph in the upper right of each frame indicates the transition probabilities from the state to the left of each bar to the state on its right, under potentiation.
  The bar graph in the lower right of each frame indicates the transition probabilities from the state to the right of each bar to the state on its left, under depression.
  The heat map in the centre right of each frame indicates the equilibrium probability distribution for each state.
  See the video for the full set of models.}\label{fig:envvid}
\end{figure}
\

@@

The derivatives, for \(m \neq n\) are
%
\begin{equation}\label{eq:finitederivs}
\begin{aligned}
  \pdiff{\CL}{\Wm^\nu_{mn}} = & \,
    \eqm_m \prn{ \brk{\thbm_m(s) - \thbm_n(s)}
     + \prn{c_m(s) + (-1)^\nu} \brk{\etwm_m(s) - \etwm_n(s)} } \\
     &+ \kktm^\nu_{mn} -  \kktm^\nu_{mm}
     + \lambda \eqm_m (\etwm_{m}(0)-\etwm_{n}(0)) 
    = 0.
\end{aligned}
\end{equation}
%
We can solve for the KKT multipliers by noting that
%
\begin{equation*}
  \kktm^\nu_{ij} \Wm^\nu_{ij} = 0,
  \qquad \text{and} \qquad
  \sum_{j: j \neq i} \kktm^\nu_{ii} \Wm^\nu_{ij} 
      = \kktm^\nu_{ii} ( - \Wm^\nu_{ii}) = r f^\nu \kktm^\nu_{ii}.
\end{equation*}
%
Then, with some new vectors defined:
%
\begin{equation}\label{eq:kktsol}
\begin{aligned}
  \kktm^\nu_{mm} &= - \eqm_m \prn{ \albm^\nu_m(s) 
    + \lambda \ombm^\nu_m(0) 
    + \prn{{c}_m(s) + (-1)^\nu} \ombm^\nu_m(s)
    }, \\
  \kktm^\nu_{mn} &= \eqm_m \big( 
      \brk{ \thbm_n(s) - \thbm_m(s) - \albm^\nu_m(s) }
    + \lambda \brk{ \etwm_n(0) - \etwm_m(0) - \ombm^\nu_m(0) } 
  \\ &\hphantom{= \eqm_m \big( }
    + \brk{{c}_m(s) + (-1)^\nu} 
        \brk{ \etwm_n(s) - \etwm_m(s) - \ombm^\nu_m(s) }
     \big), \\
  \text{where} \quad 
  \alb^\nu(s) &= \frac{\W^\nu \thb(s)}{rf^\nu}, \qquad
  \omb^\nu(s) = \frac{\W^\nu \etw(s)}{rf^\nu}.
\end{aligned}
\end{equation}
%
If we note that we can write \( \W^\nu = \prn{\frg + (-1)^\nu \enc} / 2 \), we find that
%
\begin{equation}\label{eq:diagKKT}
\begin{aligned}
  \alb^\nu(s) &= \frac{\delta\mathbf{a}(s) + (-1)^\nu \enc \thb(s)}
                     {2rf^\nu},
  \qquad 
  \omb^\nu(s) = \frac{\delta\w + s \delta\etw(s) - (-1)^\nu \mathbf{a}(s)}
                     {2rf^\nu}, 
  \\
  \kktm^\nu_{mm} &= \frac{\eqm_m}{2rf^\nu} 
    \left[ 
      \hat{A}(s) - c_m(s) (\delta\wm_m + s \delta\etwm_m(s))
      - \lambda \delta w_m
    \right. \\ &\hphantom{= \frac{\eqm_m}{2f^\nu} \big[}
    \left. {}
      + (-1)^\nu \prn{ 
        c_m(s) a_m(s) - [\encm \thbm(s)]_m
        - \delta\wm_m - s \delta\etwm_m(s)
        + \lambda a_m(0)
      }
    \right], 
\end{aligned}
\end{equation}
%
where \(\delta\) indicates mean subtraction and \(\eq \mathbf{a}(s) = \hat{A}(s)\).

@@

@@

\begin{figure}[ht]
\begin{center}
\begin{myenuma}
  \item \aligntop{\includegraphics[width=0.4\linewidth]{LenvShift.pdf}}
  \label{fig:envshift}
  \item \aligntop{\includegraphics[width=0.4\linewidth]{shift_cond.pdf}}
  \label{fig:shiftcond}
\end{myenuma}
\caption[Shifted problem vs.\ original]{Shifted problem vs.\ original.
(\ref*{fig:envshift}) Comparison of numerical optimisation of the shifted problem in \cref{eq:lshiftlagrangian,fig:envnum} with the original problemin \cref{eq:finitelagrangian}.
We see that the two approaches produce very similar numerical envelopes.
The shifted problem involves non-linear constraints and is thus harder to solve.
(\ref{fig:shiftcond}) Plot of the discrepancy in (\ref*{fig:envshift}) against the condition number of the fundamental matrix, \(\fund \).
We see that most of the large discrepancies occur where the problem is numerically ill-conditioned.
\label{fig:shifted}}
\end{center}
\end{figure}

@@

Let us define the following
%
\begin{equation}\label{eq:degenerate}
\begin{aligned}
    \dgn_{m}(s) &= \thb(s) + c_m \etw(s) + \lambda \etw(0), \\
    \qquad
    \dgn^\nu_m(s) &= \dgn_m(s) + (-1)^\nu \etw(s),   
\end{aligned}
  \implies \quad
  \pdiff{\CL}{\Wm^\nu_{mn}} = \eqm_m (\dgnm^\nu_{m,m} - \dgnm^\nu_{m,n}) + \kktm^\nu_{mn} - \kktm^\nu_{mm}.
\end{equation}
%
They should be thought of as collections of vectors rather than matrices, with the first \(m\) a label rather than an index.

Suppose that a state \(n\) has a nonzero transition rate from state \(m\) for one \(\nu\).
Then \(\kktm^\nu_{mn} = 0\) and:
%
\begin{equation}\label{eq:oneexit}
\begin{aligned}
  \Wm^\nu_{mn} > 0
  \quad \implies \quad
  \kktm^\nu_{mm} = \eqm_m (\dgnm^\nu_{m,m} - \dgnm^\nu_{m,n})
  \quad \implies \quad
  \dgnm^\nu_{m,m} &\geq \dgnm^\nu_{m,n} \\
  \text{or} \quad
  \dgnm_{m,m} - \dgnm_{m,n} &\geq - (-1)^\nu (\etwm_m - \etwm_n).
\end{aligned}
\end{equation}
%
If both \(\nu\) have nonzero rates from \(m\) to \(n\):
%
\begin{equation}\label{eq:doubleexit}
  \Wm\pot_{mn}, \Wm\dep_{mn} > 0
  \qquad \implies \qquad
  \dgnm_{m,m} - \dgnm_{m,n} \geq \abs{\etwm_m - \etwm_n}.
\end{equation}
%

@@

We use \(m*\) to label the intersection of the two diagonal lines in \cref{fig:planes}(\ref{fig:triangle_spacing}), wether or not there is a state there.
It can be defined for each \(m\), provided that it has at least one outgoing transition for each plasticity type, via
%
\begin{equation*}
\begin{lgathered}  
  \dgnm\pot_{m*} = \dgnm\pot_{m,j} = \min_k \dgnm\pot_{m,k},
  \qquad
  \dgnm\dep_{m*} = \dgnm\dep_{m,i} = \min_k \dgnm\dep_{m,k},
  \\
  \text{and also} \quad
  \dgnm_{m*} = \frac{1}{2} \prn{\dgnm\pot_{m*} + \dgnm\dep_{m*}},
  \quad
  \etwm_{m*} = \frac{1}{2} \prn{\dgnm\pot_{m*} - \dgnm\dep_{m*}},
  \quad
  \thbm_{m*} = \dgnm_{m*} - c_m \etwm_{m*}.
\end{lgathered}
\end{equation*}
%
As shown in \cref{eq:twoexits}, this produces the same point regardless of which states \(i\) and \(j\) we use, 
so long as there is a nonzero depressing/potentiating transition from \(m\) to that state.
The KKT multipliers are related to these quantities by
%
\begin{equation}\label{eq:KKTz}
  \kktm^\nu_{mm} = \eqm_m (\dgnm^\nu_{m,m} - \dgnm^\nu_{m*}),
  \qquad
  \kktm^\nu_{mk} = \eqm_m (\dgnm^\nu_{m,k} - \dgnm^\nu_{m*}).
\end{equation}
%

@@

\subsubsection{Diagonal constraints}\label{sec:diagKKT}

We can write \cref{eq:diagKKT} as
%
\begin{equation*}
\begin{aligned}
  \kktm^\nu_{mm} &= \frac{\eqm_m}{2rf^\nu} 
    \left[ 
      \hat{A}
      - (c_m + (-1)^\nu) (\delta \wm_m + s \delta \etwm_m)
      - \lambda \delta w_m
    % \right. \\ &\hphantom{= \frac{\eqm_m}{2f^\nu} }
    % \left.
      - (-1)^\nu [\encm \dgnm_m]_m
    \right],
\end{aligned}
\end{equation*}
%
with all quantities evaluated at \(s\) unless labelled otherwise.

\Cref{eq:KKTz} provides another expression for \(\kktm^\nu_{mm}\).
That expression will agree with \cref{eq:diagKKTz} provided that
%
\begin{equation}\label{eq:diagAgree}
    \hat{A} - c_m (\delta \wm_m + s \delta \etwm_m)
      - \lambda \delta w_m 
      = (\dgnm_{m,m} - \dgnm_{m*}) 
        + \Delta f (\etwm_m - \etwm_{m*}).
\end{equation}
%

@@

We have the following invariances:
%
\begin{equation*}
  A(\lambda s, \lambda \W) = A(s, \W),
  \qquad
  \CL(\lambda s, \lambda r, \lambda \W, \lambda\inv \kkt) = \CL(s, r, \W, \kkt).
\end{equation*}
%
or in differential form:
%
\begin{equation*}
  s \pdiffc<\Wm>{A}{s} + \sum_{\nu i j} \Wm^\nu_{ij} \pdiffc<s>{A}{\Wm^\nu_{ij}} 
  = 
  s \pdiffc<r \Wm \mathrlap{\kktm}>{\CL}{s} 
    + r \pdiffc<s \Wm \mathrlap{\kktm}>{\CL}{r} 
    + \sum_{\nu i j} \brk{\Wm^\nu_{ij} \pdiffc<s r \mathrlap{\kktm}>{\CL}{\Wm^\nu_{ij}} 
                      - \kktm^\nu_{ij} \pdiffc<s r {\Wm}>{\CL}{\kktm^\nu_{ij}}} = 0.
\end{equation*}
%
In \cref{eq:kktsol} we have an expression for the KKT multipliers at the maximum in terms of \(s\) and \(\W \).
We denote this expression by \( \kkt^\ddagger(s, \W) \).
If we denote the solution to the maximisation problem by \(\W^\ast(s,r), \kkt^\ast(s,r)\), we have \( \kkt^\ast(s,r) = \kkt^\ddagger(s, \W^\ast(s,r)) \) and
%
\begin{equation}\label{eq:optmodelscale}
\begin{aligned}
  \kkt^\ddagger(\lambda s, \lambda \W) 
    &= \lambda\inv \kkt^\ddagger(s, \W), &
  \qquad \text{or} \qquad
  s \pdiffc<\Wm>{\kkt^\ddagger}{s} 
      + \sum_{\nu i j} \Wm^\nu_{ij} \pdiffc<s>{\kkt^\ddagger}{\Wm^\nu_{ij}} 
    &= -\kkt^\ddagger, \\
  \W^\ast(\lambda s, \lambda r) 
    &= \lambda \W^\ast(s,r), &
  s \pdiffc<r>{\W^\ast}{s} + r \pdiffc<s>{\W^\ast}{r} 
    &= \W^\ast, \\
  \kkt^\ast(\lambda s, \lambda r) &= \lambda\inv \kkt^\ast(s,r), &
  s \pdiffc<r>{\kkt^\ast}{s} + r \pdiffc<s>{\kkt^\ast}{r} 
    &= -\kkt^\ast.
\end{aligned}
\end{equation}
%
We can also denote the envelope by \( A^\ast(s,r) = A(s, \W^\ast(s,r)) \)
%
\begin{equation*}
\begin{aligned}[t]
  A^\ast(\lambda s, \lambda r) &= A^\ast(s,r), 
  \qquad \text{or} \qquad
  s \pdiff{A^\ast}{s} + r \pdiff{A^\ast}{r} &= 0.
\end{aligned}
\end{equation*}
%
This means that the topology of the optimal model and the envelope are fixed along any of the ``rays'' of constant \(r/s\) in the \((s,r)\)-plane, as depicted in \cref{fig:planes}(\ref{fig:scaling_plane}). 
The transition probabilities of the optimal model obey a simple scaling relation along any such ray.

>>>>

Note that models with the serial topology must satisfy detailed balance.
Therefore, the conjecture from \cref{sec:finite} implies that the square-root bound of \cref{sec:sqrt} applies, implying the stricter envelope of \cref{eq:envDB}.
In \cref{fig:envnumth} we compare these theoretical envelopes with the numerical maximisation from \cref{fig:envnum}.
We can see that this conjectured envelope is close to tight, being off by a constant factor.

@@

@@

The derivatives, for \(m \neq n\) are
%
\begin{equation}\label{eq:finitederivs}
\begin{aligned}
  \pdiff{\CL}{\Wm^\nu_{mn}} = & \,
    \eqm_m \prn{ \brk{\thbm_m(s) - \thbm_n(s)}
     + \prn{c_m(s) + (-1)^\nu} \brk{\etwm_m(s) - \etwm_n(s)} } \\
     &+ \kktm^\nu_{mn} -  \kktm^\nu_{mm}
     + \lambda \eqm_m (\etwm_{m}(0)-\etwm_{n}(0)) 
    = 0.
\end{aligned}
\end{equation}
%
We can solve for the diagonal KKT multipliers by noting that
%
\begin{equation*}
  \kktm^\nu_{ij} \Wm^\nu_{ij} = 0,
  \qquad \text{and} \qquad
  \sum_{j: j \neq i} \kktm^\nu_{ii} \Wm^\nu_{ij} 
      = \kktm^\nu_{ii} ( - \Wm^\nu_{ii}) = r f^\nu \kktm^\nu_{ii}.
\end{equation*}
%
Then, with some new vectors defined:
%
\begin{equation}\label{eq:kktsol}
\begin{aligned}
  \kktm^\nu_{mn} &= \eqm_m \big( 
      \brk{ \thbm_n(s) - \thbm_m(s) - \albm^\nu_m(s) }
    + \lambda \brk{ \etwm_n(0) - \etwm_m(0) - \ombm^\nu_m(0) } 
  \\ &\hphantom{= \eqm_m \big( }
    + \brk{{c}_m(s) + (-1)^\nu} 
        \brk{ \etwm_n(s) - \etwm_m(s) - \ombm^\nu_m(s) }
     \big), \\
  \text{where} \quad 
  \alb^\nu(s) &= \frac{\W^\nu \thb(s)}{rf^\nu}, \qquad
  \omb^\nu(s) = \frac{\W^\nu \etw(s)}{rf^\nu}.
\end{aligned}
\end{equation}
%

Let us define the following
%
\begin{equation}\label{eq:dgndef}
\begin{aligned}
    \dgn_{m}(s) &= \thb(s) + c_m \etw(s) + \lambda \etw(0), \\
    \qquad
    \dgn^\nu_m(s) &= \dgn_m(s) + (-1)^\nu \etw(s),   
\end{aligned}
  \implies \quad
  \pdiff{\CL}{\Wm^\nu_{mn}} = \eqm_m (\dgnm^\nu_{m,m} - \dgnm^\nu_{m,n}) + \kktm^\nu_{mn} - \kktm^\nu_{mm}.
\end{equation}
%
They should be thought of as collections of vectors rather than matrices, with the first \(m\) a label rather than an index.

@@

\begin{figure}[tbp]
  \centering
  % Requires \usepackage{graphicx}
  \begin{myenuma}
  \item\aligntop{\includegraphics[width=0.45\linewidth,page=7]{envelope.pdf}}
  \item\aligntop{\includegraphics[width=0.45\linewidth,page=13]{envelope.pdf}}
  \item\aligntop{\includegraphics[width=0.45\linewidth,page=21]{envelope.pdf}}
  \item\aligntop{\includegraphics[width=0.45\linewidth,page=27]{envelope.pdf}}
  \item\aligntop{\includegraphics[width=0.45\linewidth,page=36]{envelope.pdf}}
  \item\aligntop{\includegraphics[width=0.45\linewidth,page=50]{envelope.pdf}}
  \end{myenuma}
  \caption[Optimal models]{The models that constitute the numeric envelope in \cref{fig:envnum}.
  The plot to the left of each frame indicates the memory curve of the model shown to the right in green, with the numeric envelope for models with the serial topology in orange and the proven envelope, \eqref{eq:env}, in blue.
  Above the left plot we have a graphical display of the model, described with more detail to the right.
  The area of each node is proportional to the steady state probability in that state and the thickness of the red and blue edges are proportional to the transition probabilities under potentiation and depression.
  The bar graph in the upper right of each frame indicates the transition probabilities from the state to the left of each bar to the state on its right, under potentiation.
  The bar graph in the lower right of each frame indicates the transition probabilities from the state to the right of each bar to the state on its left, under depression.
  The heat map in the centre right of each frame indicates the equilibrium probability distribution for each state.
  See the video for the full set of models.}\label{fig:envvid}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\begin{myenuma}
  \item \aligntop{\includegraphics[width=0.4\linewidth]{LenvShift.pdf}}
  \label{fig:envshift}
  \item \aligntop{\includegraphics[width=0.4\linewidth]{shift_cond.pdf}}
  \label{fig:shiftcond}
\end{myenuma}
\caption[Shifted problem vs.\ original]{Shifted problem vs.\ original.
(\ref*{fig:envshift}) Comparison of numerical optimisation of the shifted problem in \cref{eq:lshiftlagrangian,fig:envnum} with the original problem in \cref{eq:finitelagrangian}.
We see that the two approaches produce very similar numerical envelopes.
The shifted problem involves non-linear constraints and is thus harder to solve.
We used a limit on the condition number of \(\fund\) of \(10^3\) as a constraint during optimisation.
(\ref*{fig:shiftcond}) Plot of the discrepancy in (\ref*{fig:envshift}) against the condition number of the fundamental matrix, \(\fund \).
We see that most of the large discrepancies occur where the problem is numerically ill-conditioned.
\label{fig:shifted}}
\end{center}
\end{figure}

subsection{Diagonal constraints}\label{sec:diagKKT}

In \cref{eq:kktsol} we saw that
%
\begin{equation*}
\begin{aligned}
  \kktm^\nu_{mm} &= - \eqm_m \prn{ \albm^\nu_m(s) 
    + \lambda \ombm^\nu_m(0) 
    + \prn{{c}_m(s) + (-1)^\nu} \ombm^\nu_m(s)
    }, \\
  \text{where} \quad 
  \alb^\nu(s) &= \frac{\W^\nu \thb(s)}{rf^\nu}, \qquad
  \omb^\nu(s) = \frac{\W^\nu \etw(s)}{rf^\nu}.
\end{aligned}
\end{equation*}
%
If we note that we can write \( \W^\nu = \prn{\frg + (-1)^\nu \enc} / 2 \), we find that
%
\begin{equation}\label{eq:diagKKT}
\begin{aligned}
  \alb^\nu(s) &= \frac{\delta\mathbf{a}(s) + (-1)^\nu \enc \thb(s)}
                     {2rf^\nu},
  \qquad 
  \omb^\nu(s) = \frac{\delta\w + s \delta\etw(s) - (-1)^\nu \mathbf{a}(s)}
                     {2rf^\nu}, 
  \\
  \kktm^\nu_{mm} &= \frac{\eqm_m}{2rf^\nu} 
    \left[ 
      \hat{A}(s) - c_m(s) (\delta\wm_m + s \delta\etwm_m(s))
      - \lambda \delta w_m
    \right. \\ &\hphantom{= \frac{\eqm_m}{2f^\nu} \big[}
    \left. {}
      + (-1)^\nu \prn{ 
        c_m(s) a_m(s) - [\encm \thbm(s)]_m
        - \delta\wm_m - s \delta\etwm_m(s)
        + \lambda a_m(0)
      }
    \right], 
\end{aligned}
\end{equation}
%
where \(\delta\) indicates mean subtraction and \(\eq \mathbf{a}(s) = \hat{A}(s)\).
We can write \cref{eq:diagKKT} as
%
\begin{equation*}
\begin{aligned}
  \kktm^\nu_{mm} &= \frac{\eqm_m}{2rf^\nu} 
    \left[ 
      \hat{A}
      - (c_m + (-1)^\nu) (\delta \wm_m + s \delta \etwm_m)
      - \lambda \delta w_m
    % \right. \\ &\hphantom{= \frac{\eqm_m}{2f^\nu} }
    % \left.
      - (-1)^\nu [\encm \dgnm_m]_m
    \right],
\end{aligned}
\end{equation*}
%
with all quantities evaluated at \(s\) unless labelled otherwise.

\Cref{eq:KKTz} will provide another expression for \(\kktm^\nu_{mm}\).
That expression will agree with \cref{eq:diagKKTz} provided that
%
\begin{equation}\label{eq:diagAgree}
    \hat{A} - c_m (\delta \wm_m + s \delta \etwm_m)
      - \lambda \delta w_m 
      = (\dgnm_{m,m} - \dgnm_{m*}) 
        + \Delta f (\etwm_m - \etwm_{m*}).
\end{equation}
%

@@

The arguments in this section will break down if \(\eqm_m = 0\).
Suppose that a state \(n\) has a nonzero transition rate from state \(m\) for one \(\nu\).
Then \(\kktm^\nu_{mn} = 0\) and:
%
\begin{equation}\label{eq:oneexit}
\begin{aligned}
  \Wm^\nu_{mn} > 0
  \quad \implies \quad
  \kktm^\nu_{mm} = \eqm_m (\dgnm^\nu_{m,m} - \dgnm^\nu_{m,n})
  \quad \implies \quad
  \dgnm^\nu_{m,m} &\geq \dgnm^\nu_{m,n} \\
  \text{or} \quad
  \dgnm_{m,m} - \dgnm_{m,n} &\geq - (-1)^\nu (\etwm_m - \etwm_n).
\end{aligned}
\end{equation}
%
If both \(\nu\) have nonzero rates from \(m\) to \(n\):
%
\begin{equation}\label{eq:doubleexit}
  \Wm\pot_{mn}, \Wm\dep_{mn} > 0
  \qquad \implies \qquad
  \dgnm_{m,m} - \dgnm_{m,n} \geq \abs{\etwm_m - \etwm_n}.
\end{equation}
%

@@

We use \(m*\) to label the intersection of the two diagonal lines in \cref{fig:planes}(\ref{fig:triangle_spacing}), wether or not there is a state there.
It can be defined for each \(m\), provided that it has at least one outgoing transition for each plasticity type, via
%
\begin{equation*}
\begin{lgathered}  
  \dgnm\pot_{m*} = \dgnm\pot_{m,j} = \min_{k\neq m} \dgnm\pot_{m,k},
  \qquad
  \dgnm\dep_{m*} = \dgnm\dep_{m,i} = \min_{k\neq m} \dgnm\dep_{m,k},
  \\
  \text{and also} \quad
  \dgnm_{m*} = \frac{1}{2} \prn{\dgnm\pot_{m*} + \dgnm\dep_{m*}},
  \quad
  \etwm_{m*} = \frac{1}{2} \prn{\dgnm\pot_{m*} - \dgnm\dep_{m*}},
  \quad
  \thbm_{m*} = \dgnm_{m*} - c_m \etwm_{m*}.
\end{lgathered}
\end{equation*}
%
As shown in \cref{eq:twoexits}, this produces the same point regardless of which states \(i\) and \(j\) we use, 
so long as there is a nonzero depressing/potentiating transition from \(m\) to that state.
The KKT multipliers are related to these quantities by
%
\begin{equation}\label{eq:KKTz}
  \kktm^\nu_{mm} = \eqm_m (\dgnm^\nu_{m,m} - \dgnm^\nu_{m*}),
  \qquad
  \kktm^\nu_{mk} = \eqm_m (\dgnm^\nu_{m,k} - \dgnm^\nu_{m*}).
\end{equation}
%

@@

@@

We have the following invariances:
%
\begin{equation*}
  A(\lambda s, \lambda \W) = A(s, \W),
  \qquad
  \CL(\lambda s, \lambda r, \lambda \W, \lambda\inv \kkt) = \CL(s, r, \W, \kkt).
\end{equation*}
%
or in differential form:
%
\begin{equation*}
  s \pdiffc<\Wm>{A}{s} + \sum_{\nu i j} \Wm^\nu_{ij} \pdiffc<s>{A}{\Wm^\nu_{ij}} 
  = 
  s \pdiffc<r \Wm \mathrlap{\kktm}>{\CL}{s} 
    + r \pdiffc<s \Wm \mathrlap{\kktm}>{\CL}{r} 
    + \sum_{\nu i j} \brk{\Wm^\nu_{ij} \pdiffc<s r \mathrlap{\kktm}>{\CL}{\Wm^\nu_{ij}} 
                      - \kktm^\nu_{ij} \pdiffc<s r {\Wm}>{\CL}{\kktm^\nu_{ij}}} = 0.
\end{equation*}
%
In \cref{eq:kktsol} we have an expression for the KKT multipliers at the maximum in terms of \(s\) and \(\W \).
We denote this expression by \( \kkt^\ddagger(s, r, \W) \)
(note there is \(s\) dependance through \(\thb(s), \etw(s)\) \etc and \(r\) dependance through \(\alb\) and \(\omb\)).
If we denote the solution to the maximisation problem by \(\W^\ast(s,r), \kkt^\ast(s,r)\), we have \( \kkt^\ast(s,r) = \kkt^\ddagger(s, r, \W^\ast(s,r)) \) and
%
\begin{equation}\label{eq:optmodelscale}
\begin{aligned}
  \kkt^\ddagger(\lambda s, \lambda r, \lambda \W) 
    &= \lambda\inv \kkt^\ddagger(s, r, \W), &
  \quad \text{or} \quad
  s \pdiffc<r \mathrlap{\Wm}>{\kkt^\ddagger}{s} +
  r \pdiffc<s \mathrlap{\Wm}>{\kkt^\ddagger}{r} 
      + \sum_{\nu i j} \Wm^\nu_{ij} \pdiffc<s r>{\kkt^\ddagger}{\Wm^\nu_{ij}} 
    &= -\kkt^\ddagger, \\
  \W^\ast(\lambda s, \lambda r) 
    &= \lambda \W^\ast(s,r), &
  s \pdiffc<r>{\W^\ast}{s} + r \pdiffc<s>{\W^\ast}{r} 
    &= \W^\ast, \\
  \kkt^\ast(\lambda s, \lambda r) &= \lambda\inv \kkt^\ast(s,r), &
  s \pdiffc<r>{\kkt^\ast}{s} + r \pdiffc<s>{\kkt^\ast}{r} 
    &= -\kkt^\ast.
\end{aligned}
\end{equation}
%
We can also denote the envelope by \( A^\ast(s,r) = A(s, \W^\ast(s,r)) \)
%
\begin{equation*}
\begin{aligned}[t]
  A^\ast(\lambda s, \lambda r) &= A^\ast(s,r), 
  \qquad \text{or} \qquad
  s \pdiff{A^\ast}{s} + r \pdiff{A^\ast}{r} &= 0.
\end{aligned}
\end{equation*}
%
This means that the topology of the optimal model and the envelope are fixed along any of the ``rays'' of constant \(r/s\) in the \((s,r)\)-plane, as depicted in \cref{fig:planes}(\ref{fig:scaling_plane}). 
The transition probabilities of the optimal model obey a simple scaling relation along any such ray.
